---
title: "p8105_yh3555_hw6"
author: "Yuchen Hua"
date: "2022-11-28"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(modelr)
library(mgcv)
library(readr)
library(ggplot2)
library(patchwork)
set.seed(1)
```


## Problem 2
Import data
```{r}
homicide = read.csv("./data./homicide-data.csv")
```

Date cleaning
```{r}
homicide_clean = homicide %>%
  mutate(city_state = str_c(city, ",", state)) %>%
  mutate(city_state = as.factor(city_state)) %>%
  mutate(victim_age = as.numeric(victim_age)) %>%
  group_by(city_state, disposition) %>% 
  filter(!city_state %in% c("Dallas,TX", "Phoenix,AZ", "Kansas City,MO", "Tulsa,AL"),
         !victim_age %in% c(NA),
         !victim_sex %in% c("Unknown")) %>%
  filter(victim_race %in% c("Black", "White")) %>%
  mutate(resolved = ifelse(disposition %in% c("Closed by arrest"), 1, 0)) %>%
  select(-uid, -reported_date, -victim_last, -victim_first, -lat, -lon)
homicide_clean
```
If the case was closed by arrested, which was solved, it would be labelled as 1. If Open/No arrest or Closed without arrest, it would be labelled as 0. 

For Baltimore,MD
```{r}
baltimore_fit = homicide_clean %>%
  filter(city_state %in% c("Baltimore,MD")) %>%
  glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial())
baltimore_fit
baltimore_tidy = broom::tidy(baltimore_fit)
```
The OR and CI of baltimore can be obtained. 
```{r}
baltimore_tidy %>%
  mutate(OR = exp(estimate),
         ci_lower = exp(estimate - 1.96*std.error),
         ci_upper = exp(estimate + 1.96*std.error)) %>%
  filter(term %in% c("victim_sexMale")) %>%
  select(term, log_OR = estimate, OR, ci_lower, ci_upper) %>%
  knitr::kable(digits = 3)
```


For all cities
```{r}
nest_city = homicide_clean %>%
  nest(data = -city_state) %>%
  mutate(
    models = map(data, ~glm(resolved ~ victim_age + victim_race + victim_sex, data= ., family = binomial())),
    results = map(models, broom::tidy)) %>%
  select(-data, -models) %>%
  unnest(results) %>%
  filter(term %in% c("victim_sexMale")) %>%
  filter(term != "(Intercept)") %>%
  select(city_state, term, estimate, std.error)
```

OR an CI
```{r}
city_data = nest_city %>%
   mutate(OR = exp(estimate),
         ci_lower = exp(estimate - 1.96*std.error),
         ci_upper = exp(estimate + 1.96*std.error)) %>%
  select(term, log_OR = estimate, OR, ci_lower, ci_upper)
```

building plot
```{r}
city_data %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>%
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = ci_lower, ymax= ci_upper)) +
  facet_wrap(~term) + 
  theme(axis.text.x = element_text(angle = 80, hjust = 1))
```



## Problem 3

```{r}
bw = read.csv("./data/birthweight.csv")
```


Let's 
```{r}
bw_tidy = bw %>%
  filter(!bwt %in% c(NA),
         !momage %in% c(NA),
         !delwt %in% c(NA),
         !blength %in% c(NA),
         !fincome %in% c(NA),
         !gaweeks %in% c(NA),
         !menarche %in% c(NA),
         !mheight %in% c(NA),
         !parity %in% c(NA),
         !pnumlbw %in% c(NA),
         !pnumsga %in% c(NA),
         !ppbmi %in% c(NA),
         !ppwt %in% c(NA),
         !smoken %in% c(NA),
         !wtgain %in% c(NA)) %>%
  
  mutate(babysex = as.factor(babysex),
         malform = as.factor(malform),
         mrace = as.factor(mrace),
         frace = as.factor(frace),
         id = 1:nrow(bw))
```

Let's hypothesize that the birthweight has a linear regression relationship with head circumference, mother's weight at delivery, average number of cigarettes smoked per day during pregancy, weight gained during pregnancy. 
Let's build models. 
```{r}
mod1_lm = lm(bwt ~ blength + delwt + smoken + wtgain, data = bw_tidy)
summary(mod1_lm)
```


Let's build the models of the other two models.
```{r}
mod2_lm = lm(bwt ~ blength + gaweeks, data = bw_tidy)
summary(mod2_lm)
```

```{r}
mod3_lm = lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex, data = bw_tidy)
summary(mod3_lm)
```









